### 2020-01-07 Other/FSD_templates/Latex_Template_backup/Template/Template.tex
pd_outer_cs adjusted + some changes in the folder structure

% This is one possible realization of the official FSD Microsoft Word template. The title page has to be filled in in Microsoft Word environment and saved as a PDF file. Note, that in the header and footer the name of the author and the thesis topic have to be provided. 
%
% Compile Template in following order:
%
% pdflatex Template
% makeindex Template.nlo -s nomencl.ist -o Template.nls
% makeindex Template.acn -s Template.ist -t Template.alg -o Template.acr
% makeindex Template.glo -s Template.ist -t Template.glg -o Template.gls
% pdflatex Template
% pdflatex Template
%
%
%#################################################################################
%#################################################################################
%#################################################################################

% Preamble
\documentclass[11pt, a4paper, twoside]{report}

@@

% Set style for pages with arabic numbering 
% This block prints only the chapter number and the chapter name, not the word "Chapter"
%\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\ \thechapter. \ #1}}{}}
% Clear current page style 
\fancyhf{}
% Head (11 pt font size and 12 pt line spacing)
\fancyhf[HRE,HLO]{\includegraphics[width=2.5cm]{figs/fsd}}
\fancyhf[HRO,HLE]{\fontsize{11}{12}\selectfont \leftmark}
% Foot (11 pt font size and 12 pt line spacing)
\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Title\\First Name Last Name}
\fancyhf[FLE,FRO]{\fontsize{11}{12}\selectfont Page \thepage \thinspace / \lastpageref{LastPages}}
% Line settings
\renewcommand{\headrulewidth}{0.1pt}	%upper line
\renewcommand{\footrulewidth}{0.1pt}	%lower line

@@

% TODO
% Package for using acronyms 
%\usepackage[printonlyused]{acronym}
%\renewcommand\acsfont{\textnormal}	% Set non-bold font of the acronym units

@@

% Package for edditing TOC, LOF and LOT
\usepackage[titles]{tocloft}

@@

% Package for acronyms
\usepackage[acronym, automake, nopostdot, nogroupskip]{glossaries}
\setlength{\LTleft}{-0.15cm}			% left justified
\renewcommand*{\arraystretch}{1.4}		% vertical distance between entries, default is 1
% List
\newacronym{ADF}{ADF}{Automatic Direction Finder}
\newacronym{ADI}{ADI}{Automatic Direction Indicator}
% Make gls
\renewcommand*\entryname{Acronym}
\makeglossaries

% Package for setting up the list of symbols
%https://tex.stackexchange.com/questions/112884/how-to-achieve-nomenclature-entries-like-symbol-description-dimension-and-uni
\usepackage{nomencl,etoolbox,ragged2e,siunitx}
%
\newcommand{\DimensUnits}[2]{\makebox[1em]{#1}\makebox[4em]{#2\hfill}\ignorespaces}
\newcommand{\insertnomheaders}{\item[\bfseries Symbol]\DimensUnits{}{\textbf{Unit}}\textbf{Description}}
%
\renewcommand\nomgroup[1]{%
  \item[\large\bfseries
  \ifstrequal{#1}{A}{Acronyms}{%
  \ifstrequal{#1}{B}{Latin Letters}{%
  \ifstrequal{#1}{G}{Greek Letters}{%
  \ifstrequal{#1}{S}{Indices}{% 
  \ifstrequal{#1}{U}{Subscripts}{%   
  \ifstrequal{#1}{X}{Other Symbols}{}}}}}}]
  \insertnomheaders
  }
%
\renewcommand*{\nompreamble}{\markboth{\nomname}{\nomname}}
% parbox - Description
\newcommand{\nomdescr}[1]{\parbox[t]{10cm}{\RaggedRight #1}}
\newcommand{\nomwithdim}[5]{\nomenclature[#1]{#2}{\DimensUnits{}{#5}\nomdescr{#3}}}
%
\makenomenclature

%#################################################################################%#################################################################################%#################################################################################

\begin{document}

@@

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Statutory Declaration}

@@

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Abstract}

@@

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Table of Contents}

@@

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{List of Figures}

@@

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{List of Tables}

@@

% Print table of acronyms
\printglossary[type=\acronymtype, title={Table of Acronyms}, nonumberlist, style=longheader]

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Table of Acronyms}

%Insert empty page after table of acronyms
\newpage\null\thispagestyle{empty}

% Add Table of Symbols
%\chapter*{Table of Symbols} \label{sec:symbols}
\mbox{}
\nomwithdim{B}{\( F \)}{Force}{L}{$N$}
\nomwithdim{B}{\( g \)}{Gravitational acceleration}{}{$m/s^2$}
\nomwithdim{G}{\( \alpha \)}{Angle of attack}{}{$rad$}
\nomwithdim{G}{\( \zeta \)}{Damping of a linear second order system}{}{--}
\nomwithdim{S}{\( m \)}{Variable related to pitch moment}{}{}
\nomwithdim{S}{\( W \)}{Wind}{}{}
\renewcommand{\nomname}{Table of Symbols}
\printnomenclature[6em]

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Table of Symbols}

%Insert empty page after table of symbols
\newpage\null\thispagestyle{empty}\newpage

@@

% Activate default fancy design (chapter number, chapter)
\pagestyle{fancy} 
\renewcommand{\chaptermark}[1]{\markboth{\ \thechapter \ #1}{}}

@@

The bibliography is to be included according to the IEEE style, and references to sources are preferably to be included in square brackets \cite{Handbook}, \cite{Cooper}. The respective bibliography item has to describe the source clearly without ambiguity and citations from sources have to be marked with quotation marks.

@@

Reference to equation \ref{eq:eq_1}. (Cross-reference, Reference Type: Equation, Insert reference to: entire caption) 
The following section 2 contains further example text, figures, tables and equations. 
In section 3 some concluding remarks can be found. Here, we use the acronym \acrfull{ADF}. The second acronym is \acrfull{ADI}. After the first usage of the 1st acronym, only the short version is used: \acrshort{ADF}.

@@

% Add references
\renewcommand\bibname{References}		% Rename Bibliography to References
\bibliographystyle{plain}
\bibliography{Literature}

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{References}

>>>>

% This is one possible realization of the official FSD Microsoft Word template. The title page has to be filled in in Microsoft Word environment and saved as a PDF file. Note, that in the header and footer the name of the author and the thesis topic have to be provided. 
%
% TODOs:
% - Write instructions (what and where to fill in)
%
% - References 
% - Style of the List of Symbols

%#################################################################################
% Preamble
\documentclass[11pt, a4paper, twoside]{report}

@@

% Set style for pages with arabic numbering 
% This block prints only the chapter number and the chapter name, not the word "Chapter"
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\ \thechapter. \ #1}}{}}
% Clear current page style 
\fancyhf{}
% Head (11 pt font size and 12 pt line spacing)
\fancyhf[HRE,HLO]{\includegraphics[width=2.5cm]{figs/fsd}}
\fancyhf[HRO,HLE]{\fontsize{11}{12}\selectfont \leftmark}
% Foot (11 pt font size and 12 pt line spacing)
\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Title\\First Name Last Name}
\fancyhf[FLE,FRO]{\fontsize{11}{12}\selectfont Page \thepage \thinspace / \lastpageref{LastPages}}
% Line settings
\renewcommand{\headrulewidth}{0.1pt}	%upper line
\renewcommand{\footrulewidth}{0.1pt}	%lower line

@@

% Package for using acronyms 
\usepackage[printonlyused]{acronym}
\renewcommand\acsfont{\textnormal}	% Set non-bold font of the acronym units

@@

% Package for setting space between units in TOC, LOF...
\usepackage[titles]{tocloft}

@@

% Package for edditing TOC, LOF and LOT
\usepackage{tocloft}

%#################################################################################
\begin{document}

@@

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
\chaptermark{Statutory Declaration}

@@

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
\chaptermark{Abstract}

@@

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
\chaptermark{Table of Contents}

@@

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
\chaptermark{List of Figures}

@@

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
\chaptermark{List of Tables}

@@

% Add Table of Acronyms 
\chapter*{Table of Acronyms} \label{sec:acronyms}
\textbf{Acronym}\hspace{3.3cm}\textbf{Description}
\vspace*{-2mm}	% vertical space 
\begin{acronym}[ADF\hspace{4cm}]\itemsep=0pt 	% in [] supposed to be the largest word
	\acro{ADF}{Automatic Direction Finder}
	\acro{ADI}{Automatic Direction Indicator}
\end{acronym}

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
\chaptermark{Table of Acronyms}

%Insert empty page after table of acronyms
\newpage\null\thispagestyle{empty}\newpage

% Add Table of Symbols
\chapter*{Table of Symbols} \label{sec:symbols}

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
\chaptermark{List of Symbols}

%Insert empty page after table of acronyms
\newpage\null\thispagestyle{empty}\newpage

@@

% Activate default fancy design (chapter number, chapter)
\pagestyle{fancy} 
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\ \thechapter. \ #1}}{}}

@@

The bibliography is to be included according to the IEEE style, and references to sources are preferably to be included in square brackets \cite{Alberi2017}. The respective bibliography item has to describe the source clearly without ambiguity and citations from sources have to be marked with quotation marks.

@@

Reference to equation \ref{eq:eq_1}. (Cross-reference, Reference Type: Equation, Insert reference to: entire caption) 
The following section 2 contains further example text, figures, tables and equations. In section 3 some concluding remarks can be found. Here, we use the acronym \ac{ADF}. The second acronym is \ac{ADI}. After the first usage of the 1st acronym, only the short version is displayed: \ac{ADF}.

@@

% Add references
%\renewcommand\bibname{References}		% Rename Bibliography to References
%\bibliographystyle{plain}

### 2020-01-07 Paper_EV/Paper_EV.tex
pd_outer_cs adjusted + some changes in the folder structure

% This is one possible realization of the official FSD Microsoft Word template. The title page has to be filled in in Microsoft Word environment and saved as a PDF file. Note, that in the header and footer the name of the author and the thesis topic have to be provided. 
%
% Compile Template in following order:
%
% pdflatex Paper_EV
% makeindex Paper_EV.nlo -s nomencl.ist -o Paper_EV.nls (Table of Symbols)
% makeindex Paper_EV.acn -s Paper_EV.ist -t Paper_EV.alg -o Paper_EV.acr (Table of Acronyms)
% makeindex Paper_EV.glo -s Paper_EV.ist -t Paper_EV.glg -o Paper_EV.gls
% pdflatex Paper_EV
% pdflatex Paper_EV
%
%
%#################################################################################
%#################################################################################
%#################################################################################

@@

@@

@@

@@

@@

\subsection{Structure} \label{subsec:Structure}

@@

>>>>

% This is one possible realization of the official FSD Microsoft Word template. The title page has to be filled in in Microsoft Word environment and saved as a PDF file. Note, that in the header and footer the name of the author and the thesis topic have to be provided. 
%
% Compile Template in following order:
%
% pdflatex Paper_EV
% makeindex Paper_EV.nlo -s nomencl.ist -o Paper_EV.nls (Table of Symbols)
% makeindex Paper_EV.acn -s Paper_EV.ist -t Paper_EV.alg -o Paper_EV.acr (Table of Acronyms)
% makeindex Paper_EV.glo -s Paper_EV.ist -t Paper_EV.glg -o Paper_EV.gls
% pdflatex Paper_EV
% pdflatex Paper_EV
%
% TODO:
% - Title page: Dr. -> Dr. ir.
%
%#################################################################################
%#################################################################################
%#################################################################################

@@

\section{General Equations of Motion} \label{sec:eqs_motion}
General: \\
- Linear Momentum\\
- Angular Momentum\\
- Attitude differential equations\\
- Position differential equations\\
- External forces and moments

with some of the used assumptions

@@

- Theory from Sieberling paper.

@@

- Here only the general principle is provided, next subsections show the full derivation of the two controller loops.

\subsection{INDI inner loop} \label{subsec: indi_inner}

- Derivation of the inner INDI loop (detailed equations).

\subsection{INDI outer loop} \label{subsec: indi_outer}

- Derivation of the outer INDI loop (detailed equations).

@@

- Some facts about Crazyflie hardware (foto, uC frequency, weight, length)

@@

- Estimation of relevant components (Matrices...)\\
- Testing of the PD-gains\\
- Testing the filter

\subsection{Structure} \label{subsec:Structure}
- Parameters\\
- Actuator dynamics\\
- Filter\\
- Images of the Simulink model

@@

\subsection{Structure of the Code} \label{subsec:structure_ofthe_code}
